Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-06-30 gtx_algorithm.tex
mention a spanner variant of galaxy tree

>>>>

A variant of the \gtx{} algorithm as a whole we did not explore so much in practice is its ability
to produce spanner by stopping early. Basically if we stop at iteration $t$, we output the graph
$G_t$ (which in general is not a tree) with its edges unfolded to lie in $E_0$. This corresponds to
a trade off between having more edges than $|V_0|-1$ but potentially making shorter connection and
thus having a lower stretch.
